Title

### 2023-10-19 Article.tex
Commit before changing min/max to min/range

In order to have a better understanding of the implementation of the VUHARD subroutine, we are going to detail the procedure used to compute the flow stress and the three derivatives in one step as a function of the triplet of input values~$\varepsilon$, $\mdot{\varepsilon}$, $T$.
We suppose that the current input is stored in a three components vector $\overrightarrow{\xi}$, with $\xi_1=\varepsilon$, $\xi_2=\log(\mdot{\varepsilon}/\mdot{\varepsilon}_0)$ and~$\xi_3=T$.
We also suppose that the minimum and maximum values of the inputs, used during the learning phase, are stored in two vectors $\overrightarrow{\xi}_{min}$ and $\overrightarrow{\xi}_{max}$ respectively. The minimum and maximum values of the stress are also stored in two variables $\sigma_{min}$ and $\sigma_{max}$ respectively.
\begin{itemize}
\item We first use Equation (\ref{eq:ANN-input}) to compute the vector $\overrightarrow{x}$ where all components of $\overrightarrow{\xi}$ will be remapped within the range $[0,1]$. 
\begin{equation}
\overrightarrow{x}=\left(\overrightarrow{\xi}-\overrightarrow{\xi}_{min}\right)\oslash\Delta\overrightarrow{\xi},
\end{equation}
where $\oslash$ is the Hadamard division operator and $\Delta\overrightarrow{\xi}=\overrightarrow{\xi}_{max}-\overrightarrow{\xi}_{min}$.
\item Conforming to Equation (\ref{eq:ANN-y}), we compute the vector:
\begin{equation}
\overrightarrow{y}\lay{1}=\w\lay{1}\cdot\overrightarrow{x}+\overrightarrow{b}\lay{1}.
\end{equation} 
\item Then, from Equation (\ref{eq:ANN-f}) and the expression of the activation function used for the first layer of the ANN and defined by one of the Equations (\ref{eq:act-sig}-\ref{eq:act-exp}), we compute the vector:
\begin{equation}
\overrightarrow{\hat{y}}\lay{1}=f\lay{1}(\overrightarrow{y}\lay{1}).
\end{equation} 
\item We repeat the process for the second layer, so that we compute the vectors: \begin{equation}
\overrightarrow{y}\lay{2}=\w\lay{2}\cdot\overrightarrow{\hat{y}}\lay{1}+\overrightarrow{b}\lay{2},
\end{equation} 
and:
\begin{equation}
\overrightarrow{\hat{y}}\lay{2}=f\lay{2}(\overrightarrow{y}\lay{2}).
\end{equation} 
\item From Equations (\ref{eq:ANN-s}) and (\ref{eq:ANN-output}), we compute the flow stress $\sigma$ using the following equation:
\begin{equation}
s = \Delta\sigma.\left(\overrightarrow{w}^T \dotp \overrightarrow{\hat{y}}\lay{2} + b\right) + \sigma_{min}
\end{equation} 
with $\Delta\sigma = \sigma_{max}-\sigma_{min}$.
\item Then we can compute in a single step the three derivatives $\overrightarrow{\sigma}'$ from Equation (\ref{eq:ANN-der}) with the following expression:
\begin{equation}
\overrightarrow{\sigma}' = \Delta\sigma.\w\lay{1}^T \dotp\left[\left(\w\lay{2}^T \dotp \left(\overrightarrow{w}^T \circ f'(\overrightarrow{y}\lay{2})\right)\right) \circ f'(\overrightarrow{y}\lay{1})\right] \oslash \left(\Delta\overrightarrow{\xi} \circ \overrightarrow{u}\right),
\end{equation}
where $\overrightarrow{u}^T=[1,\mdot{\varepsilon},1]$.
\end{itemize}

\begin{figure}[H]
\begin{PythonListing}%[float,floatplacement=H]
def AnnFunctionWithDerivatives(xi, act, dact):
    xi[1,:] = np.log(xi[1,:] / deps0)
    x = (xi - xi_min) / delta_xi
    y1 = w1.dot(x) + b1
    h1 = act(y1)
    y2 = w2.dot(h1) + b2
    h2 = act(y2)
    sigma = (w3.dot(h2) + b3) * delta_sig + sig_min
    dsigma = (w1.T).dot((w2.T).dot(w3.T * dact(y2)) 
    	* dact(y1)) * delta_sig / delta_xi
    dsigma[1,:] = dsigma[1,:] / xi[1,:]
    return sigma, dsigma 
\end{PythonListing}
\caption{L}
\end{figure}

>>>>

In order to have a better understanding of the implementation of the VUHARD subroutine, we are going to detail the procedure used to compute the flow stress and the three derivatives in one step as a function of the triplet of input values~$\varepsilon$, $\mdot{\varepsilon}$, $T$.
We suppose that the current input is stored in a three components vector $\overrightarrow{\xi}^T=\left[\varepsilon, \log(\mdot{\varepsilon}/\mdot{\varepsilon}_0), T\right]$.
We also suppose that the minimum and maximum values of the inputs, used during the learning phase, are stored in two vectors $\overrightarrow{\xi}_{min}$ and $\overrightarrow{\xi}_{max}$ respectively. The minimum and maximum values of the stress are also stored in two variables $\sigma_{min}$ and $\sigma_{max}$ respectively.
\begin{itemize}
\item We first use Equation (\ref{eq:ANN-input}) to compute the vector $\overrightarrow{x}$ where all components of $\overrightarrow{\xi}$ will be remapped within the range $[0,1]$:
\begin{equation}
\overrightarrow{x}=\left(\overrightarrow{\xi}-\overrightarrow{\xi}_{min}\right)\oslash\Delta\overrightarrow{\xi},
\end{equation}
where $\oslash$ is the Hadamard division operator and $\Delta\overrightarrow{\xi}=\overrightarrow{\xi}_{max}-\overrightarrow{\xi}_{min}$.
\item Conforming to Equation (\ref{eq:ANN-y}), we compute the vector:
\begin{equation}
\overrightarrow{y}\lay{1}=\w\lay{1}\cdot\overrightarrow{x}+\overrightarrow{b}\lay{1}.
\end{equation} 
\item Then, from Equation (\ref{eq:ANN-f}) and the expression of the activation function used for the first layer of the ANN and defined by one of the Equations (\ref{eq:act-sig}-\ref{eq:act-exp}), we compute the vector:
\begin{equation}
\overrightarrow{\hat{y}}\lay{1}=f\lay{1}(\overrightarrow{y}\lay{1}).
\end{equation} 
\item We repeat the process for the second layer, so that we compute the vectors: \begin{equation}
\overrightarrow{y}\lay{2}=\w\lay{2}\cdot\overrightarrow{\hat{y}}\lay{1}+\overrightarrow{b}\lay{2},
\end{equation} 
and:
\begin{equation}
\overrightarrow{\hat{y}}\lay{2}=f\lay{2}(\overrightarrow{y}\lay{2}).
\end{equation} 
\item From Equations (\ref{eq:ANN-s}) and (\ref{eq:ANN-output}), we compute the flow stress $\sigma$ using the following equation:
\begin{equation}
s = \Delta\sigma.\left(\overrightarrow{w}^T \dotp \overrightarrow{\hat{y}}\lay{2} + b\right) + \sigma_{min}
\end{equation} 
with $\Delta\sigma = \sigma_{max}-\sigma_{min}$.
\item Then we can compute in a single step the three derivatives $\overrightarrow{\sigma}'$ from Equation (\ref{eq:ANN-der}) with the following expression:
\begin{equation}
\begin{array}{l}
\overrightarrow{\Sig}' = \Delta\sigma.\w\lay{1}^T \dotp\left[\left(\w\lay{2}^T \dotp \left(\overrightarrow{w}^T \circ f'(\overrightarrow{y}\lay{2})\right)\right) \circ f'(\overrightarrow{y}\lay{1})\right] \oslash \Delta\overrightarrow{\xi}\\
\Sig_2' := \Sig_2' / \mdot{\varepsilon}
\end{array},
\end{equation}
where the expression used for $f'()$ changes depending on the activation function used.
\end{itemize}

\begin{figure}[H]
\begin{PythonListing}
def stressAndDerivatives(xi, act, dact):
  x = xi
  x[1] = log(x[1] / deps0)
  x = (x - xi_min) / delta_xi
  y1 = w1.dot(x) + b1
  yh1 = act(y1)
  y2 = w2.dot(yh1) + b2
  yh2 = act(y2)
  stress = delta_sig * (w3.dot(yh2) + b3) + sig_min
  dstress = delta_sig * ((w1.T).dot((w2.T).dot(w3.T * dact(y2)) 
  	* dact(y1))) / delta_xi
  dstress[1] = dstress[1] / xi[1]
  return stress, dstress 
\end{PythonListing}
\caption{L}
\end{figure}
